\thetitle

### 2013-04-19 tfpie/tfpie.tex
something for all of 4

>>>>

Finally, at the end of the course, we are able to build on the two
major segments to examine less-well-explored topics in object-oriented
programming.  Typically, we cover the basics of implementing OO
programming in a functional language, advanced OO techniques such as
mixins and prototypes, and a new OO language such as Ruby or
JavaScript.  Additionally, we emphasize the ability to embed
functional programming in an OO context, using techniques such as the
command pattern and the visitor patterns.  Again, the key message is
the transferability of concepts across languages.
